### 2019-12-27 Sections/cryptowars.tex
qds now has references.

@@

QDS schemes are inspired Lamport's one-time signatures \cite{}.  Here we assume a classical 
one-way function $f$. For such a function, given $x$, it is easy to evaluate $f(x)$. However, it is hard to invert to find $x$ from $f(x)$. The algorithm is as follows
\begin{enumerate}
\item Key generation: Alice chooses two random inputs $x_0$ and $x_1$, and evaluates $f(x_0)$, $f(x_1)$. She publically broacasts the pair $(0,f(x_0))$, $(1,f(x_1))$ whilst keeping $x_0, x_1$ secret. 
\item Signing: Alice sends the message $b$ along with her stored corresponding secret key $x_b$.
\item Verification: the receivers evaluate $f(x_b)$ and check if this agrees with the public key in order to choose to accept or reject.
\end{enumerate}

@@

In 2001, Gottesman and Chuang \cite{} proposed the first QDS protocol. The idea is to use
the non-orthogonality of state to realize a ``quantum one-way function", where the difficulty to invert the function is based on the laws of physics rather than computational complexity.

@@

Quantum memory - the storage of the quantum state until verification renders the scheme impractical. The idea is to replace the quantum public key with a classical verification key, which is now different for all the receivers \cite{}.

After removing the quantum memory requirement, the other experimentally challenging task is ensuring that the same quantum public key was send to different receivers. This step can be bypassed by adding an extra step, replacing the state comparison SWAP test with a "symmetrization". This step ensures that even if the states distributed by Alice are not identical, the classical verification keys shared by the receivers will be symmetric.

% We explain the the symmetrization protocol here: Alice selectsx

@@

Now we are able to describe a memory-less QDS protocol that can be realized with the same technology as QKD. The protocol works for three parties, but can be generalised.

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function QDS():
\begin{enumerate}
% 
	\item Key generation: Alice performs the first part of a QKD protocol separately, twice with
	Bob and Charlie. Alice has has four bit strings $A_0^B, A_1^B, A_0^C, A_1^C$, Bob has two strings $K_0^B, K_1^B$, and Charlie has $K_0^C, K_1^C$. The private key $sk$ is the concatenation of the two corresponding strings, $sk=(A_0^B||A_0^C, A_1^B||A_1^C)$. At this stage, error rates of the quantum channel are estimated.
	% 
	\item Bob and Charlie perform a symmetrization by exchanging secretly half of their strings (via another QKD link). The new strings for Bob are $S_0^B, S_1^B$ and Charlie $S_0^C,S_1^C$. They are composed from half of the string initially sent to Bob and half of that to Charlie,, but which part from Bob and Charlie's initial strings is unknown to Alice.
	% 
	\item The verification keys for Bob and Charlie are $pk_B = (S_0^B,S_1^B)$, and 
	      $pk_C=(S_0^C,S_1^C)$.
	% 
	\item Signing: to sign a message $M$, Alice sends $(M, A_M^B||A_M^C)$ to Bob.
	% 
	\item Verification: Bob checks the mismatch rate between the signature received 
	      $A_M^B||A_M^C$ and his stored verification key $S_M^B$. If the error is compatible with the channel noise, he accepts. Charlie receives a message with Alice's signature, but from Bob. He performs a similar check and may choose to accept the message as having originated from Alice. 
\item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{A quantum digital signature (QDS) protocol compatible with a QKD network.}\label{alg:qds}
\end{table}

>>>>

\subsubsection{Saturation attacks on the detector}

The security proofs of CV-QKD assume a linear relationship between the quadratures of the state and the measurements, but in reality, homodyne detection have a finite range of linearity. The detectors can be saturated \cite{pirandola2019advances}. By causing Bob's measurement results to overlap with the saturation region, Eve can artificially reduce the trusted parties' error estimation.

Proposed countermeasures include using a Gaussian post-selection filter to ensure that the measurement results used for key generation fall within the linear region of the detector, and to use random attentuation of Bob's signal to monitor whether the measurements are linearly related to the inputs \cite{bib:qin2016pra}

@@

QDS schemes are inspired Lamport's one-time signatures \cite{lamport1979constructing}.  Here we assume a classical 
one-way function $f$. For such a function, given $x$, it is easy to evaluate $f(x)$. However, it is hard to invert to find $x$ from $f(x)$. The algorithm is as follows
\begin{enumerate}
\item Key generation: Alice chooses two random inputs $x_0$ and $x_1$, and evaluates $f(x_0)$, $f(x_1)$. She publically broacasts the pair $(0,f(x_0))$, $(1,f(x_1))$ whilst keeping $x_0, x_1$ secret. 
\item Signing: Alice sends the message $b$ along with her stored corresponding secret key $x_b$.
\item Verification: the receivers evaluate $f(x_b)$ and check if this agrees with the public key in order to choose to accept or reject.
\end{enumerate}

@@

In 2001, Gottesman and Chuang \cite{gottesman2001quantum} proposed the first QDS protocol. The idea is to use
the non-orthogonality of state to realize a ``quantum one-way function", where the difficulty to invert the function is based on the laws of physics rather than computational complexity.

@@

The storage of the quantum state until verification renders the scheme impractical. This requirement can be removed by replacing the quantum public key with a classical verification key, which is now different for all the receivers \cite{bib:Dunjko2014prl}.
After removing the quantum memory requirement, the other experimentally challenging task is ensuring that the same quantum public key was send to different receivers. This step can be bypassed by adding an extra step, replacing the state comparison SWAP test with a "symmetrization" \cite{bib:Wallden2015pra}. This step ensures that even if the states distributed by Alice are not identical, the classical verification keys shared by the receivers will be symmetric.

We explain the the symmetrization protocol here: Alice generates two sets of BB84 states and sends them to Bob and Charlie respectively. Bob (Charlie) either measures it or forwards it to Charlie (Bob), and he similarly measures the states he receives from Charlie (Bob). Depending on the outcome, Bob knows for certainty which state Alice did \textit{not} send. For example, if the measurement outcome is $\ket{0}$, he knows for sure Alice did not send $\ket{1}$. Bob stores the sequence of eliminated state, and whether it was received directly from Alice or Charlie. This classical information will be Bob's (Charlie's) verification key.

@@

Now we are able to describe a memory-less QDS protocol that can be realized with the same technology as QKD. The protocol works for three parties, but can be generalised. In this protocol, Alice signs the message, Bob first receives the message and needs to authenticate it, and Charlie receives the forwarded message from Bob, and verifies that the initial source was indeed Alice.

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function QDS():
\begin{enumerate}
% 
	\item Key generation: Alice performs the first part of a QKD protocol separately, twice with
	Bob and Charlie. Alice has has four bit strings $A_0^B, A_1^B, A_0^C, A_1^C$, Bob has two strings $K_0^B, K_1^B$, and Charlie has $K_0^C, K_1^C$. The private key $sk$ is the concatenation of the two corresponding strings, $sk=(A_0^B||A_0^C, A_1^B||A_1^C)$. At this stage, error rates of the quantum channel are estimated.
	% 
	\item Bob and Charlie perform a symmetrization by exchanging secretly half of their strings (via another QKD link). The new strings for Bob are $S_0^B, S_1^B$ and Charlie $S_0^C,S_1^C$. They are composed from half of the string initially sent to Bob and half of that to Charlie, but Alice does not know from which parts of Bob's and Charlie's strings they came from.
	% 
	\item The verification keys for Bob and Charlie are $pk_B = (S_0^B,S_1^B)$, and 
	      $pk_C=(S_0^C,S_1^C)$.
	% 
	\item Signing: to sign a message $M$, Alice sends $(M, A_M^B||A_M^C)$ to Bob.
	% 
	\item Verification: Bob checks the mismatch rate between the signature received 
	      $A_M^B||A_M^C$ and his stored verification key $S_M^B$. If the error is compatible with the channel noise, he accepts. Charlie receives a message with Alice's signature, but from Bob. He performs a similar check and may choose to accept the message as having originated from Alice. 
\item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{A quantum digital signature (QDS) protocol compatible with a QKD network.}\label{alg:qds}
\end{table}
